SoK: Web Application Attack Defenses (in Question)

### 2014-10-10 docs/questioning.tex
minor changes

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2} and Angelos Keromytis\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Network Security Lab\\
Department of Computer Scinence\\
Columbia University\\
\{dimitro, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Software Engineering and Security Lab\\
Department of Management Science and Technology\\
Athens University of Economics and Business\\
louridas@aueb.gr
}}

@@

  \multirow{3}{*}{Parse-Tree Validation}

@@

	\multirow{12}{*}{Policy Enforcement}

@@

@@

\begin{table*}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.99}{
    \begin{tabular}{l|c|ccc}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
	&& \bf{Source Code}
	& \bf{Executable}
	& \bf{Testbed} \\
    \hline
	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
	% &  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
    &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline    
	\multirow{12}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
    &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
	&   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
	&   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline  
        \multirow{11}{*}{Training}
    &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\sc ao} & {\sc na} \\
	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & {\bf ?} & {\bf ?} & {\bf ?} \\
	& 	{\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
    \end{tabular}}
    \begin{tablenotes}
	\begin{footnotesize}
       \item[1] The check mark (\tick) indicates that some point within
       the publication there is a homepage where the reader can refer to, to
       download the corresponding software. {\sc ao} (Available On-line) suggests
       that the software is available on-line but the
       address was not mentioned in the paper, which probably indicates that
       the authors made it available after the publication. The question ({\bf ?})
       mark, indicates that the a homepage for the software was included
       in the publication but now it is not available.
	\end{footnotesize}
    \end{tablenotes}
    \caption{Availability of the corresponding mechanisms.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2},
Michalis Polychronakis,\IEEEauthorrefmark{1}
and Angelos Keromytis\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Network Security Lab\\
Department of Computer Scinence\\
Columbia University\\
\{dimitro, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Software Engineering and Security Lab\\
Department of Management Science and Technology\\
Athens University of Economics and Business\\
louridas@aueb.gr
}}

@@

  \multirow{2}{*}{Parse-Tree Validation}

@@

  \multirow{3}{*}{Code Rewriting}

@@

	\multirow{10}{*}{Policy Enforcement}

@@

\begin{table*}
    \begin{tabular}{l|c|ccc}
    & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
	&& \bf{Source Code}
	& \bf{Executable}
	& \bf{Testbed} \\
	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
	% &  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
    &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
  \multirow{2}{*}{Parse-Tree Validation}
  &   {\it {\sc sqlc}heck}~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
  \multirow{3}{*}{Code Rewriting}
  &   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
  &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
	\multirow{10}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
  &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
	&   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\sc ao} & {\sc na} \\
	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & {\bf ?} & {\bf ?} & {\bf ?} \\
	& 	{\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
       \item[1] The check mark (\tick) indicates that some point within
       the publication there is a homepage where the reader can refer to, to
       download the corresponding software. {\sc ao} (Available On-line) suggests
       that the software is available on-line but the
       address was not mentioned in the paper, which probably indicates that
       the authors made it available after the publication. The question ({\bf ?})
       mark, indicates that the a homepage for the software was included
       in the publication but now it is not available.
    \caption{Availability of the corresponding mechanisms.}
\end{table*}
